Latex-rendered version of the main text of ``How environmental drivers of spatial synchrony interact''

### 2023-06-27 Paper/Paper.Rnw
small

%Get line numbers to work, also in figure captions
\linenumbers
\DeclareCaptionFont{linenumbers}{\internallinenumbers}
\captionsetup[figure]{font+=linenumbers} % use \internallinenumbers inside figure caption

\doublespacing

@@

%header material for paper
\title{How environmental drivers of spatial synchrony interact}
\date{}

@@

\newpage

\large{\textbf{How environmental drivers of spatial synchrony interact}}

>>>>

%Get line numbers to work, also in figure captions
%\linenumbers
%\DeclareCaptionFont{linenumbers}{\internallinenumbers}
%\captionsetup[figure]{font+=linenumbers} % use \internallinenumbers inside figure caption

%\doublespacing

@@

%header material for paper
\title{Latex-rendered version of the main text of ``How environmental drivers of spatial synchrony interact''}
\date{}

@@
